Intrusion Detection with Genetic Algorithms and Fuzzy Logic

### 2013-10-13 paper.tex
Wrote some things in the KDD99 data set section.

\subsection{False Positives and False Negatives}
\emph{False positives} and \emph{False negatives} are two values that are used to evaluate the accuracy of an intrusion detection system. A false positive happens when an intrusion detection system incorrectly identifies normal activity as being an attack. A false negative happens when an intrusion detection system fails to identify harmful activity.~\cite{Liao201316}

@@

\subsection{KDD99 Data Set}

>>>>

@@

\subsection{KDD99 Data Set}
Knowledge Discovery in Databases (KDD) is the process of extracting useful and interesting information from data in order to understand patterns in the data, with a limited amount of human intervention. Data is collected from several different sources and then is analyzed in order to produce patterns or models over the data.~\cite{bc1_ecindm} The KDD99 data set is a benchmark data set that was simulated in a military network environment in 1998, and then it was formed into the KDD99 data set in 1999~\cite{6559603}. In an experiment, the researchers divide the data set into two subsets, a \emph{training set} and a \emph{testing set}. Algorithms are trained on the training set to look for patterns. These patterns are then verified when the testing set is used.~\cite{bc1_ecindm} Four different measures are then used to determine the accuracy of an algorithm, which are described in Secion~\ref{sec:PosNeg}.

\subsection{False Positives, False Negatives, True Positives, True Negatives}
\label{sec:PosNeg}
\emph{False positives} and \emph{False negatives} are two values that are used to evaluate the accuracy of an intrusion detection system. A false positive happens when an intrusion detection system incorrectly identifies normal activity as being an attack. A false negative happens when an intrusion detection system fails to identify harmful activity.~\cite{Liao201316}

\mycomment{Write more here}
